Human-Computer Mobile Distributed Computing for Time Series Forecasting\thanks{This work was supported with private funding by Velbazhd Software LLC.}

### 2019-09-05 Human-Computer-Mobile-Distributed-Computing-for-Time-Series-Forecasting/paper.tex
Initial Springer revision.

\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx,DCCN2019_en}
\usepackage{placeins}

\pagestyle{fancy}
\fancyhead{} 
\fancyfoot{}

\usepackage[utf8]{inputenc}
\linespread{1.0}

\usepackage{amsmath}

\makeatletter
\fancyhead[RO]{\small DCCN 2019 \\ {23-27 September 2019}}
\fancyhead[LO]{\small Ketipov, Kostadinov, Petrov, Zankinski, Balabanov \\ Human-Computer MDC for TS Forecasting}
% Rumen Ketipov
% Georgi Kostadinov
% Plamen Petrov
% Iliyan Zankinski
% Todor Balabanov

\c@page=1

\makeatother

\title{Human-Computer Mobile Distributed Computing for Time Series Forecasting}

\author[1]{\small R.R. Ketipov}
\author[1]{\small G.B. Kostadinov}
\author[1]{\small P.D. Petrov}
\author[1]{\small \\I.A. Zankinski}
\author[0000-0003-3139-069X]{\small T.D. Balabanov}

\affil[1]{\footnotesize Institute of Information and Communication Technologies (IICT) \break Bulgarian Academy of Sciences (BAS) \break acad. Georgi Bonchev Str., block 2, 1113 Sofia, Bulgaria}

\email{rketipov@iit.bas.bg, g.kostadinov@iit.bas.bg, p.petrov@iit.bas.bg, iliyan@hsi.iccs.bas.bg, todorb@iinf.bas.bg}

@@

\udc{004.93}

{\let\newpage\relax\maketitle}

\vskip -1.5em

\footnotetext{This work was supported with private funding by Velbazhd Software LLC.}

@@

\keywords{distributed computing, time series forecasting, artificial neural networks, evolutionary algorithms}
\end{abstract}

@@

\vskip 1.5em

\begin{thebibliography}{99}

\bibitem{nava01} Nava, N., Di Matteo, T., Aste, T., \textbf{\textit{Financial Time Series Forecasting Using Empirical Mode Decomposition and Support Vector Regression}}, RISKS, \textbf{6}(1), article 7, 2018.

@@

\bibitem{tashev01} Tashev, T., Hristov, H., \textbf{\textit{Modeling of synthesis of information processes with generalized nets}}, Cybernetics and Information Technologies, \textbf{3}(2), p. 92--104, 2003.

\end{thebibliography}

>>>>

\documentclass[runningheads]{llncs}

\usepackage{graphicx}
\usepackage{placeins}

@@

\title{Human-Computer Mobile Distributed Computing for Time Series Forecasting\thanks{This work was supported with private funding by Velbazhd Software LLC.}}

\author{
	Rumen Ketipov \and
	Georgi Kostadinov \and
	Plamen Petrov \and \\
	Iliyan Zankinskir \and
	Todor Balabanov\orcidID{0000-0003-3139-069X}
}
% Rumen Ketipov - rketipov@iit.bas.bg
% Georgi Kostadinov - g.kostadinov@iit.bas.bg
% Plamen Petrov - p.petrov@iit.bas.bg
% Iliyan Zankinski - iliyan@hsi.iccs.bas.bg
% Todor Balabanov - todorb@iinf.bas.bg

\authorrunning{R. Ketipov et al.}

\institute{
	Institute of Information and Communication Technologies \\ 
	Bulgarian Academy of Sciences \\ 
	acad. Georgi Bonchev Str., block 2, 1113 Sofia, Bulgaria \\
	\email{iict@bas.bg} \\  
	\url{http://iict.bas.bg/}
}

\maketitle

@@

\keywords{Distributed computing \and Time series forecasting \and Artificial neural networks \and Evolutionary algorithms.}
\end{abstract}

@@

\begin{thebibliography}{8}
\bibitem{nava01} Nava, N., Di Matteo, T., Aste, T., \textbf{\textit{Financial Time Series Forecasting Using Empirical Mode Decomposition and Support Vector Regression}}, RISKS, \textbf{6}(1), article 7, 2018.

@@

\bibitem{tashev01} Tashev, T., Hristov, H., \textbf{\textit{Modeling of synthesis of information processes with generalized nets}}, Cybernetics and Information Technologies, \textbf{3}(2), p. 92--104, 2003.
\end{thebibliography}
